The Impact of ChatGPT news on MSFT

### 2023-12-02 MSFT.Rmd
Included gitIgnore and tinytex

# Insert introduction here

@@

```{r echo=FALSE, include=TRUE}
if (!require("vars")) install.packages("vars", dependencies=TRUE)
if (!require("tseries")) install.packages("tseries", dependencies=TRUE)
if (!require("quantmod")) install.packages("quantmod", dependencies=TRUE)
if (!require("PerformanceAnalytics")) install.packages("PerformanceAnalytics", dependencies=TRUE)
if (!require("forecast")) install.packages("forecast", dependencies=TRUE)
if (!require("rugarch")) install.packages("rugarch", dependencies=TRUE)

library(PerformanceAnalytics)
library(forecast)
library(rugarch)
library(vars)
library(tseries)
library(quantmod)

MSFT <- getSymbols.yahoo("MSFT", from="2022-01-01", to="2023-12-01", periodicity = "daily", auto.assign=FALSE)[,6]

@@

```{r echo=FALSE, include=TRUE}
coeftest(VAR_est)
#MSFT_VAR <- VAR(cbind(MSFT_returns, ChatGPT), ic="AIC", lag.max = 24)

>>>>

```{r include=FALSE}
if (!require("vars")) install.packages("vars", dependencies=TRUE)
if (!require("tseries")) install.packages("tseries", dependencies=TRUE)
if (!require("quantmod")) install.packages("quantmod", dependencies=TRUE)
if (!require("PerformanceAnalytics")) install.packages("PerformanceAnalytics", dependencies=TRUE)
if (!require("forecast")) install.packages("forecast", dependencies=TRUE)
if (!require("rugarch")) install.packages("rugarch", dependencies=TRUE)

library(PerformanceAnalytics)
library(forecast)
library(rugarch)
library(vars)
library(tseries)
library(quantmod)
library(tinytex)
```
# Insert introduction here

@@

```{r echo=FALSE, include=TRUE}
MSFT <- getSymbols.yahoo("MSFT", from="2022-01-01", to="2023-12-01", periodicity = "daily", auto.assign=FALSE)[,6]

@@

```{r echo=FALSE, include=TRUE}
#MSFT_VAR <- VAR(cbind(MSFT_returns, ChatGPT), ic="AIC", lag.max = 24)
#coeftest(MSFT_VAR)
```
